---
title: "PracticalMachineLearning"
author: "Songju Kim"
date: '2020 7 6 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading files

```{r echo=TRUE}

train_url <-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
test_url<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

raw_train_set<-read.csv(train_url)
raw_test_set <-read.csv(test_url)

dim(raw_train_set)


```
160 variables!! Too many.

We check data structures with str and summary R function,
Then We notice there are so many variables which are NA or None values.

## Preprocessing 

Before slicing, we preprocess raw data set into tidy set

With nearZeroVar function, we throw away predictors which are not qualified.
Additionally, We reduce predictors which is almost composed of NAs


```{r pressure, echo=TRUE}
library(caret)

NZV<-nearZeroVar(raw_train_set)

train_set<-raw_train_set[,-NZV]
test_set <-raw_test_set[,-NZV]

Na90<-sapply(train_set,function(x) mean(is.na(x))) >0.9 
train_set<-train_set[,Na90==FALSE]
 

```
First 5 column variables are not meaningful for model
So, throw away~~!

```{r echo=TRUE}

train_set<-train_set[,-(1:5)]

test_set<-test_set[,Na90==FALSE]

test_set<-test_set[,-(1:5)]

train_set$classe<-as.factor(train_set$classe)


```

## Split train data for cross validation

We split train data set into 2 sets for cross validation

```{r echo=TRUE}
library(caret)

inTrain <-createDataPartition(train_set$classe,p=0.75,list=FALSE) 
strain_set<-train_set[inTrain,]
stest_set<-train_set[-inTrain,]
```

## Model selection and Train 

I selected rpart regression tree model for this problem.
We need to classify categorical outcome based on numeric predictors.

```{r echo=TRUE}
library(rattle)

mod_rpart <- train(classe ~ .,  method = "rpart",  data = train_set,   tuneLength = 50,   metric = "Accuracy" )

fancyRpartPlot(mod_rpart$finalModel)

```


## Test and cross validation
```{r echo=TRUE}

predMod<-predict(mod_rpart,stest_set)


confusionMatrix(predMod,stest_set$classe)
```


## Results of Actual test

```{r echo=TRUE}
testMod<-predict(mod_rpart,test_set)


ggplot(data.frame(problem_id=test_set$problem_id,classe=testMod),aes(x=problem_id,y=classe,col=classe))+geom_point()
```

